\sectionTitle{Experience}{\faSuitcase}

\begin{projects}
	\wideexperience
	{PCB Project Manager • Challenger Solutions - Chelmsford, UK}
	{june 2019 - \textbf{current}}
	{\begin{itemize}
    \item Working as part of the rapidly growing Box Build department at
      Challenger Solutions, I am in charge of the Rotolight NEO2 project.
    \item My day to day duties involve the organisation of the build team,
      stock control and reporting of current progress, and reporting all
      relevant information and figures to the line manager.
    \item Assisting with the constant development and improvements
      within the company and externally with Rotolight to develop their
      upcoming projects.
  \end{itemize}}

	\\
  \\

% 	--------------------------------------------------------------------

	\wideexperience
	{Race Director • Brentwood Karting - Brentwood, UK}
	{march 2014 - \textbf{current}}
	{\begin{itemize}
    \item When I was on shift as the race director my duties included
      ensuring the smooth running of all activities throughout the day,
      dealing with any customer queries or complaints, delegating
      responsibilities to the race marshals and making sure all health and
      safety checks and briefs were carried out.
    \item Alongside my main role I also helped to ensure that all facilities are
      maintained and customer areas were clean and tidy., I worked as a
      trainee race mechanic for both the car and kart racing sides of the
      race team.
  \end{itemize}}

	\\
  \\

% 	--------------------------------------------------------------------

	\wideexperience
	{Small Engine Machanic/Forklift Operator/General Labourer • AJB Diesel - St Peters, Australia}
	{spetember 2018 - may 2019}
	{\begin{itemize}
    \item Working as part of the AJB team, I am in charge of
      servicing/repairing all small engine tools that may come into the
      workshop such as lawn mowers, chainsaws, concrete saws etc.
    \item As well as being in charge of this area of the business, I also had a
      range of other responsibilities including general labour around the
      workshop, delivering/picking up parts from all over Sydney, and I
      am the forklift operator for the company having to carry out tasks
      such as lifting/removing engines, moving stock etc.
  \end{itemize}}

	\\
  \\

% 	--------------------------------------------------------------------

	\wideexperience
	{Lead Generation • First Data - Chelmsford, UK}
	{february 2018 - september 2018}
	{\begin{itemize}
    \item As part of a very large payment processing company I worked as
      part of the lead generation team.
    \item This was a very fast paced role as we were targeted and had
      incentives based on number of calls and other areas daily/weekly
      and monthly.
  \end{itemize}}

	\\
  \\

% 	--------------------------------------------------------------------

	\wideexperience
	{Sales Executive • Glyn Hopkin Nissan - Chelmsford, UK}
	{march 2017 - september 2017}
	{\begin{itemize}
    \item As part of the sales team I worked within the showroom selling new
      and approved pre-owned Nissan vehicles.
    \item This job required me to work to strict sales targets, as well as
      building and maintaining existing customer relations, and meeting
      with new customers throughout the working day.
  \end{itemize}}

\\
\\

% 	--------------------------------------------------------------------

  \wideexperience
  {Medical Repair Technician • Olympus Keymed - Southend-On-Sea, UK}
  {february 2015 - march 2017}
  {\begin{itemize}
    \item Part of the Technical Services team, I carried out complex repairs
      on Endoscopes and other medical cameras.
    \item I have been trained to obtain my repair licence, and my role
      demanded strict organisation, attention to detail and hygiene as we
      were working on equipment that was used inside the human body.
    \item During my time working at Olympus I have obtained a good
      understanding on how endoscopes work internally and how to
      investigate and diagnose electrical and mechanical issues with the
      scopes.
  \end{itemize}}

\end{projects}
